aaaa

### 2023-10-31 outputs/paper/paper.qmd
Finalize all the models

acs <- read.csv(here("outputs/data/merged_data_acs.csv"))
acs_covid <- read.csv(here("outputs/data/merged_data_acs_covid.csv"))
data <- read.csv(here("outputs/data/merged_data_overall.csv"))
map_data <- read.csv(here("outputs/data/merged_data_overall.csv"))
data <- data %>%
  mutate(pctile = ntile(mean_household_income, 100),
         party = case_when(rep_win == 1 ~ "Republican",
                             rep_win == 0 ~ "Democratic",
                             TRUE ~ "A"),
         rep_rate = (votes_rep/total_votes)*1000) %>% 
  filter(state != "AK")
data_model <- data %>% 
  select(-county, -state, -total_population, -females, -fips, -cases, -deaths,
         -votes_rep, -votes_dem, -total_votes, -infection_rate, -mean_household_income)

@@

```{r plot-chunk, fig.width=8, fig.height=6, out.width="80%"}
#| echo: false
#| message: false
#| fig-cap: Number

@@

# Second plot
plot2 <- plot_usmap(data = data, values = "party", regions = "counties", exclude = "AK") + 
  scale_fill_manual(values = c("Republican" = "red", "Democratic" = "blue"), 
                    name = "Party",
                    breaks = c("Republican", "Democratic")) + 
  labs(subtitle = "Subtitle for Plot 2") +
  theme(legend.position = "right", plot.title = element_blank())

@@

# Creating the Model
best1 <- lm(death_rate ~ prop_higher_education + pctile + no_insurance +
               males + old_85 + white_pct + black_pct, 
            data = training_data)

broom::tidy(best1) %>% 
  mutate(predictors = c("(Intercept)", as.character(attr(terms(best1), "term.labels"))),
         estimate = round(estimate, 2),
         std.error = round(std.error, 2),
         statistic = round(statistic, 2),
         p.value = round(p.value, 3)) %>% 
  select(predictors,
         estimate,
         std.error,
         statistic,
         p.value) %>% 
  rename(`Predictor` = predictors,
         `Estimate` = estimate,
         `Standard Error` = std.error,
         `Statistics` = statistic,
         `P-value` = p.value) %>% 
  kable(format = "latex")
```
@first-model shows the summary table for the model without political references. Using the above information, we can write the equation model:

@@

# Creating the Model
best2 <- lm(death_rate ~ rep_rate + rep_win * prop_higher_education + pctile + 
                 private_insurance  + no_insurance +
                 males + old_85  + rep_win*white_pct + 
                 black_pct, data = training_data)

@@

\begin{align*}
\text{Death Rate} &=  7.7507490 \\
& + 0.0034980 \times \text{Rep\_Rate} \\
& - 0.4972847 \times \text{Rep\_Win} \\
& - 0.0120727 \times \text{Prop\_Higher\_Education} \\
& - 0.0099034 \times \text{Pctile} \\
& - 0.0284321 \times \text{Private\_Insurance} \\
& + 0.0281570 \times \text{No\_Insurance} \\
& - 0.0593644 \times \text{Males} \\
& + 0.3024402 \times \text{Old\_85} \\
& - 0.0169198 \times \text{White\_Pct} \\
& + 0.0130027 \times \text{Black\_Pct} \\
& - 0.0172526 \times \text{Rep\_Win:Prop\_Higher\_Education} \\
& + 0.0125389 \times \text{Rep\_Win:White\_Pct}
\end{align*}

The difference between the second and the first model is that the

@@

## First discussion point {#sec-first-point}

@@

## Second discussion point

## Third discussion point

@@

# Appendix {-}
## Model details
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

social1 <- lm(death_rate ~ prop_higher_education, data = training_data)
economic1 <- lm(death_rate ~ pctile + unemployment + no_insurance +
                             private_insurance + public_insurance, 
                data = training_data)
demographic1 <- lm(death_rate ~ males + old_85 + children + old_65 +
                                white_pct + black_pct, data = training_data)
overall1 <- lm(death_rate ~ .-rep_win - party - rep_rate, data = training_data)
best1 <- lm(death_rate ~ prop_higher_education + pctile + no_insurance +
               males + old_85 + white_pct + black_pct, 
            data = training_data)
modelsummary(list(social1, economic1, demographic1, overall1, best1), stars=TRUE)
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

social2 <- lm(death_rate ~ rep_rate + rep_win * prop_higher_education, data = training_data)
economic2 <- lm(death_rate ~ rep_rate + pctile + unemployment + no_insurance +
                             rep_win*private_insurance + public_insurance, 
                data = training_data)
demographic2 <- lm(death_rate ~ rep_rate + males + old_85 + children + old_65 +
                                rep_win*white_pct + black_pct, data = training_data)
overall2 <- lm(death_rate ~ rep_rate + rep_win * prop_higher_education + pctile + 
                 unemployment + rep_win*private_insurance + public_insurance + no_insurance +
                 males + old_85 + children + old_65 + rep_win*white_pct + 
                 black_pct, data = training_data)
best2 <- lm(death_rate ~ rep_rate + rep_win * prop_higher_education + pctile + 
                 private_insurance  + no_insurance +
                 males + old_85  + rep_win*white_pct + 
                 black_pct, data = training_data)
modelsummary(list(social2, economic2, demographic2, overall2, best2), stars=TRUE)
```

>>>>

acs <- read.csv(here("outputs/data/merged_data_acs.csv"))
acs_covid <- read.csv(here("outputs/data/merged_data_acs_covid.csv"))
data <- read.csv(here("outputs/data/merged_data_overall.csv"))
map_data <- read.csv(here("outputs/data/merged_data_overall.csv"))
data <- data %>%
  mutate(pctile = ntile(mean_household_income, 100),
         party = case_when(rep_win == 1 ~ "Republican",
                             rep_win == 0 ~ "Democratic",
                             TRUE ~ "A"),
         rep_rate = (votes_rep/total_votes)*1000,
         high_income = case_when(pctile > 50 ~ 1,
                                 TRUE ~ 0)) %>% 
  filter(state != "AK")
data_model <- data %>% 
  select(-county, -state, -total_population, -females, -fips, -cases, -deaths,
         -votes_rep, -votes_dem, -total_votes, -infection_rate, -mean_household_income, -old_65)

@@

```{r plot-chunk, fig.width=8, fig.height=6, out.width="100%"}
#| echo: false
#| message: false
#| fig-cap: Number

@@

# Second plot
plot2 <- plot_usmap(data = data, values = "party", regions = "counties", exclude = "AK", "Hawaii") + 
  scale_fill_manual(values = c("Republican" = "red", "Democratic" = "blue"), 
                    name = "Party",
                    breaks = c("Republican", "Democratic")) + 
  labs(subtitle = "Subtitle for Plot 2") +
  theme(legend.position = "right", plot.title = element_blank())

@@

@first-model shows the summary table for the model without political references. Using the above information, we can write the equation model:

```{r}
model1 <- lm(death_rate ~ prop_higher_education + pctile + no_insurance + private_insurance + males + old_85 + white_pct + black_pct, data = training_data)
summary(model1)
```

```{r}
model2 <- lm(death_rate ~ rep_rate + prop_higher_education + pctile + 
                 private_insurance  + no_insurance +
                 males + old_85  + white_pct + 
                 black_pct, data = training_data)
summary(model2)
```

@@

@@

\begin{align*}
\text{Death Rate} &=  7.75 \\
& + 0.0034980 \times \text{Rep\_Rate} \\
& - 0.4972847 \times \text{Rep\_Win} \\
& - 0.0120727 \times \text{Prop\_Higher\_Education} \\
& - 0.0099034 \times \text{Pctile} \\
& - 0.0284321 \times \text{Private\_Insurance} \\
& + 0.0281570 \times \text{No\_Insurance} \\
& - 0.0593644 \times \text{Males} \\
& + 0.3024402 \times \text{Old\_85} \\
& - 0.0169198 \times \text{White\_Pct} \\
& + 0.0130027 \times \text{Black\_Pct} \\
& - 0.0172526 \times \text{Rep\_Win:Prop\_Higher\_Education} \\
& + 0.0125389 \times \text{Rep\_Win:White\_Pct}
\end{align*}

The difference between the second and the first model is that the second model includes the political preference for each county as one predictor to predict the death rate due to COVID. Holding other variables, we can see that every 100 more votes for republican party, 0.3 more people are expected to dead. In addition, if the county votes for the Republican, then it is expected to have

@@

## The impact of political preference on death rate is more significant than expected.

@@

## However, the socio-economic variables especially the private insurance, also play an important role.

## The importantance matrix matches our models

@@

# Appendix {-}

## Model details

aaa

ojnoj

klmko

# Creating the Model
best1 <- lm(death_rate ~ prop_higher_education + pctile + no_insurance + private_insurance + males + old_85 + white_pct + black_pct, data = training_data)

broom::tidy(best1) %>% 
  mutate(predictors = c("(Intercept)", as.character(attr(terms(best1), "term.labels"))),
         estimate = round(estimate, 2),
         std.error = round(std.error, 2),
         statistic = round(statistic, 2),
         p.value = round(p.value, 3)) %>% 
  select(predictors,
         estimate,
         std.error,
         statistic,
         p.value) %>% 
  rename(`Predictor` = predictors,
         `Estimate` = estimate,
         `Standard Error` = std.error,
         `Statistics` = statistic,
         `P-value` = p.value) %>% 
  kable(format = "latex")
```

j jnjn

# Creating the Model
best2 <- lm(death_rate ~ rep_rate + prop_higher_education + pctile + 
                 private_insurance  + no_insurance +
                 males + old_85  + white_pct + 
                 black_pct, data = training_data)

```{r}
#| echo: false
#| message: false
#| tbl-cap: Summary of the set of models with political preferences

@@

social1 <- lm(death_rate ~ prop_higher_education, data = training_data)
economic1 <- lm(death_rate ~ pctile + unemployment + no_insurance +
                             private_insurance + public_insurance, 
                data = training_data)
demographic1 <- lm(death_rate ~ males + old_85 + children +
                                white_pct + black_pct, data = training_data)
overall1 <- lm(death_rate ~ .-rep_win - party - rep_rate, data = training_data)
best1 <- lm(death_rate ~ prop_higher_education + pctile + no_insurance + private_insurance + males + old_85 + white_pct + black_pct, data = training_data)
modelsummary(list(social1, economic1, demographic1, overall1, best1), stars=TRUE)
```

```{r}
#| echo: false
#| message: false
#| label: tbl-modelresults
#| tbl-cap: Summary of the set of models with political preferences

social2 <- lm(death_rate ~ rep_rate + prop_higher_education, data = training_data)
economic2 <- lm(death_rate ~ rep_rate + pctile + unemployment + no_insurance +
                             private_insurance + public_insurance, 
                data = training_data)
demographic2 <- lm(death_rate ~ rep_rate + males + old_85 + children +
                                white_pct + black_pct, data = training_data)
overall2 <- lm(death_rate ~ rep_rate + prop_higher_education + pctile + 
                 unemployment + private_insurance + public_insurance + no_insurance +
                 males + old_85 + children + white_pct + 
                 black_pct, data = training_data)
best2 <- lm(death_rate ~ rep_rate + prop_higher_education + pctile + 
                 private_insurance  + no_insurance +
                 males + old_85  + white_pct + 
                 black_pct, data = training_data)
modelsummary(list(social2, economic2, demographic2, overall2, best2), stars=TRUE)
```
